Title field: summary

### 2021-01-29 inst/examples/title.Rmd
added uniquetitles plot
updated title page

>>>>

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$title)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
p <- ggplot(d, aes(x = n)) +
       geom_histogram() +
       scale_x_log10() +
       scale_y_log10() +
       labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```
